---
title: "Inferences Questions"
author: "Isaiah Patino"
date: "3 November 2025"
format: html
embed-resources: true
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(rstatix)
library(ggpubr)
carseats <- ISLR2::Carseats
```

## Problem 1 
Does this data provide evidence against the company’s claim that the average price of their own seats is $110? Follow all best practices from class, including hypotheses, a relevant visualization, and a conclusion in non-technical language.

The null hypothesis μ = $110 and the alternate hypothesis 
μ ≠ $110. 
```{r}
ggplot(carseats, aes(sample = Price)) +
  geom_qq() + 
  geom_qq_line(color = "blue") +
  labs(title = "Q-Q Plot for Car Seat Prices",
       x = "Sample Quantities",
       y = "Theoretical Quantities")
```
## Problem 2 
Compute a level 90% confidence interval for the mean competitor price in the population from which this sample is drawn. What is the sample mean? What is the margin of error?
```{r}
get_summary_stats(carseats["Price"], type = "mean_sd")

result <- t.test(carseats$Price, mu = 110, conf.level = 0.90)
result

error <- 115.795 - 110
error
```
The sample mean is $115.80 and the margin of error is 5.80.

## Problem 3 
Use these tools to create a table with counts of penguin species and home islands in the penguins set. Include marginal counts in your table.
```{r}
penguins <- penguins

peng_table <- table(penguins$species, penguins$island)
addmargins(peng_table)
```

## Problem 4 
Push your solutions to this set to your GitHub page, including both the Quarto source and the rendered html. Use file names of the form, “math250_nov5_yourname.”

Provide a clickable link to the repository on your personal GitHub where these files can be found.



